Diffusive Homeostasis in a Self-Organizing Recurrent Neural Network \\ \begin{large} Spatially dependent Interaction as a Determinant of Neural Activity and Plasticity \end{large}

### 2017-03-06 draft.tex
.

\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/mat_sim_std_dev_dist.png}

@@

\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/mat_sim_skew_dist.png}

@@

\caption{Comparison of distribution of standard deviation (A) and skewness (B) for random-matrix solutions (gray) and values acquired from simulation (blue), Neumann boundaries.}

@@

In summary, shape and broadness of the firing rate distribution appeared to be strongly determined by fluctuation in the spatial distribution of neurons. To further back up this result we arranged excitatory neurons on a regular grid with a nearest-neighbor distance of $\mathrm{50\, \mu m}$ and a $\mathrm{25\, \mu m}$ distance between the border and the neurons closest to it. By doing so all neurons were given the same structure of neighbors. We expected that all neurons then should---in theory---exhibit the exact same firing rate due to symmetry. Figure \ref{Fir_Rate_Dist_Reg_Grid} shows the result, being a significantly narrower distribution. This strongly supported the previous assertion.
%% plot_firing_rate_dist_regular_grid.py
\includegraphics[width=0.7\textwidth]{../../plots/firing_rate_dists/regular_grid_firing_rate_dist.png}
\caption{Distribution of firing rates for a regular square grid with distance $\mathrm{50\, \mu m}$ and Neumann boundary conditions, $\mathrm{D=10\,\mu m^2 ms^{-1}}$.}
\label{Fir_Rate_Dist_Reg_Grid}

\subsubsection{Low-Density Neighborhoods correlate with strong outgoing Connections}
In Section \ref{Section_Mean_outgoing_Weights} we stated that diffusive homeostasis allowed the network do develop few neurons with exceptionally strong outgoing weights. We found this effect to be present in neurons with an highly above-average firing rate. Moreover, the outcomes presented in Section \ref{Section_Rand_Mat_vs_Sim} suggest that the steady state of firing rates is strongly influenced by the spatial structure of excitatory neurons. Combining these two qualities led us the conclusion that one should be able to observe some relation between spatial structure and the emergence of ``driver neurons". More specific, regions of neurons with above average firing rates should develop stronger outgoing connections. To get an intuitive understanding of what characterizes regions of above-average firing rates we interpreted the homeostatic condition in the high-neuron-density limit as an approximation of a continuous integral equation:
\begin{equation}
\int d^2 x' \rho(\mathbf{x}') r(\mathbf{x}') \psi(|\mathbf{x}-\mathbf{x}'|) = NO_0 \; , \; \forall \, \mathbf{x}
\label{Density_Limit_Hom}
\end{equation}
where $\mathrm{\rho(\mathbf{x})}$ is the local neuron density and $\mathrm{r(\mathbf{x})}$ the local firing rate. Here we assumed that our tissue is of infinite size and thus the integral is carried out over $\mathbb{R}^2$. In this form the solution for $\mathrm{r(\mathbf{x})}$ is quite trivial:
\begin{equation}
r(\mathbf{x}) = \frac{NO_0}{\rho(\mathbf{x}) \int d^2 x' \psi(|\mathbf{x}'|)} \propto \frac{1}{\rho(\mathbf{x})} \; .
\label{Density_Limit_Hom_Solution}
\end{equation}
Combined with the fact that the logarithm of outgoing excitatory weights correlates with excitatory firing rate (see Figure \ref{Out_Weight_vs_F}), this led us to the conclusion that low density regions should correlate with strong outgoing weights and vice versa. We approximated the local neuron density by means of a a Gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$ to test this hypothesis. Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} shows the results. Despite a certain amount of randomness, our prediction was indeed verified. 
\begin{figure}
%% density_vs_sum_out_weights.py
\includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights.png}
%% density_vs_sum_out_weights_points.py
\includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights_points.png}
\caption{(A) and (B): Scatter plot of inverse of local neuron density (calculated by convolution with a gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$) and decadic logarithm of outgoing excitatory weights. Note the spatial correlation in high/low-density regions. (C) and (D): The decadic logarithm of outgoing weights correlates with inverse neuron density (corr. coeff. of 0.513).}
\label{Inverse_Dens_vs_Sum_Out_Weights}
\end{figure}

\newpage
\subsection{Spreading of NO-sources extends Encoding of Input Heterogeneity}
We considered the possibility that a wider spread of each individual NO-source could locally decrease distinguishability between neurons since our analytic results revealed that a strong correlation between spatial structure and result firing rates is present if diffusive interaction allows a clear distinction between individual neurons and their spatial neighbors. Thereby it might allow input heterogeneities to be encoded over a longer period of time without the need to tweak diffusion to unrealistically high values. The biological plausibility of this idea is discussed in Section \ref{Possible_Modifications_Section}.

To test our hypothesis, we modified our model such that each neuron released nitric oxide evenly into a circular area with a radius of $\mathrm{50 \, \mu m}$, centered around the neuron's position. The homeostatic readout was still taken solely from the centering point. Thereafter, we ran the same simulation as for Figure \ref{Ext_Input_Switch}. Comparing both plots, we saw a much greater persistence of distinction between excitatory subgroups. The time course of activity suggests that this distinction might even be permanent and steady instead of a very slow but transient state.
\begin{figure}
%% spread_source_illustration.py
\includegraphics[width=\textwidth]{../../plots/spread_source_illustration.png}
%% plot_external_input_switch_activity_spread_source.py
\includegraphics[width=\textwidth]{../../plots/external_input_switch_spread_source.png}
\caption{A/B: Illustration of circular kernels used for NO-insertion, overlay of all 400 neurons (left) and a single example (right). C: Resulting activity for excitatory subgroups. All settings were kept the same as for Figure \ref{Ext_Input_Switch}.}
\label{External_Input_Switch_Spread_Source}
\end{figure}

@@

\subsection{Homeostatic Stability}
Though being unintended in our recurrent network, the occurrence and necessary analysis of persistent oscillations led to a better understanding of their origin and the need for slow timescales of homeostatic adaptation. In another theoretical study Harnack et al. treated the necessity of slow homeostatic adaptation in a more general fashion \cite{Stability_Homeostasis_Harnack_2015}. Among other results it is reported that increasing the number of dynamic variables in a feedback system decreases its stability. This is in line with the fact that our previously used single-cell homeostatic control (see Equation \eqref{can_hom_rate}) exhibited no instabilities since it only incorporated firing thresholds as dynamic variables. In contrast, diffusive homeostasis increased the dimensionality of the system by means of its NO-synthesis and diffusion pathway. Harnack et al. additionally reported a similar effect as seen in our system: Noise can reduce stability in a damped dynamical system by constantly causing deviations from its fixed point.

@@

\subsection{The Firing Rate Distribution} \label{Fir_Rate_Dist_Discussion_Section}
By implementing diffusive homeostasis into the LIF-SORN model we managed to achieve a broader, skewed firing rate distribution while preserving appreciated features of network topology. Though the distribution did approximately resemble a log-normal-like shape, it did not perfectly match our expectations. In order to acquire a deeper understanding of the mechanisms that determine these statistics we developed an analytical expression that allowed us to reliably predict the steady state of firing rates based on the spatial structure of excitatory neurons. We would like to emphasize that this explanation differs from common approaches of understanding the emergence of heavy-tailed statistics of firing rates in recurrent networks. Theoretical studies on the behavior of recurrent networks are largely based on the assumption that the excitability of neurons is not individually fine-tuned but rather randomly distributed and adjusted globally to achieve a desired mean firing rate. Predictions about the resulting activity are then made based on (potentially simplified) statistical features of recurrent connectivity and the specific form of the neuronal transfer function used in the model, see e.g. \cite{Roxin_Firing_Rate_Distribution,Vreeswijk1998}. Our interpretation of our results leads to the conclusion that this canonical approach matches the limiting case of instant diffusion: While Figures \ref{Fir_Rate_Dist_Instant_compare} and \ref{Fir_Rate_Dist_Compare} did not reveal many differences in terms of overall statistics, the decorrelation discussed in Section \ref{Section_Rand_Mat_vs_Sim} and plotted in Figure \ref{Corr_Coeff_vs_D} suggests that increasing the diffusion constant goes along with a transition between a spatially determined configuration of excitatory firing rates and a network topology-determined behavior.

@@

Instead, we hypothesized that we might be able to uncouple activity from spatial structure without tweaking the diffusion process by spatially increasing the spread of NO-insertion. While Sweeney et al. argued that the size of the studied tissue is large compared to the size of individual somata (which, apparently, they claim to be the main source of nitric oxide) Philippides et al. reported that NO is often synthesized in a more delocalized way by means of fine fibers exceeding the soma \cite{Philippides_2005}. The diameter of these ``production areas" is on the order of $\mathrm{10-100 \mu m}$. To incorporate this spread of synthesis in our model of diffusion we convolved a circular shaped and shifted production-kernel (multiplied by the momentary rate of NO-synthesis) with the field of NO-concentration. Intuitively, it locally smeared the distinction between neighboring neurons. From a more abstract point of view, it provided a way to drive the matrix defined in Equation \eqref{NO_equil_cond_interact_matrix_operator} towards singularity, allowing for more states of activity to approximately fulfill the homeostatic target. As Figure \ref{External_Input_Switch_Spread_Source} suggests, this indeed improved flexibility of individual activity while retaining an overall constant firing rate. We therefore gained further control over the strictness of the homeostatic mechanism by adjusting the area of NO insertion.

@@

Taking a closer look at the distributions depicted in Figure \ref{Weight_Dist} we noted that the increased width of the distribution is largely due to to an increment on the left half of the curve. Since new weights are initialized at $\mathrm{10^{-4}\, mV}$ this might indicate that some weights are drifting much more slowly from their value of initialization compared to other weights. These ``slow drifters" are presumably connecting neurons both spiking at a below-average firing rate.
This provides an explanation why this effect is more present in the case of diffusive homeostasis since it causes a portion of neurons to have rather low firing rates. On the other hand, for non-diffusive homeostasis, one can assume that the amount of STDP-fluctuations is approximately equal for all recurrent excitatory weights because of the fixation of firing rates.

@@

As an indirect consequence of spatial structure determining activity (as discussed in Section \ref{Fir_Rate_Dist_Discussion_Section}) we found that neurons with a low-density neighborhood have a higher chance of developing these strong outgoing weights. Since this effect is directly linked to the low-density/high-firing-rate relation shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (C), all previous thoughts regarding plausibility similarly apply to this result: \emph{If} a relationship between density and firing rates existed, we could indeed argue to also expect a relation as shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (D), since it is known that neurons with above-average firing rates tend to undergo long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.

>>>>

\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/mat_sim_std_dev_dist_new.png}

@@

\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/mat_sim_skew_dist_new.png}

@@

\caption{Comparison of distribution of standard deviation (A) and skewness (B) for random-matrix solutions (gray) and values acquired from simulation (blue), Neumann boundaries. Same simulation data as in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} was used, each point representing a single simulation. The histograms for the analytic solutions were generated for 50 $\rm D$ values, spanning equally between $\rm D=0 mu m^2 /ms$ and $\rm D=20 mu m^2 /ms$. Each column is a histogram of $\rm 200$ firing-rate solutions for randomly generated positions, giving a total of $\rm 10000$ matrix solutions.}

@@

In summary, shape and broadness of the firing rate distribution appeared to be strongly determined by fluctuations in the spatial distribution of neurons.

To further back up this result we arranged excitatory neurons on a regular grid with a nearest-neighbor distance of $\mathrm{50\, \mu m}$ and a $\mathrm{25\, \mu m}$ distance between the border and the neurons closest to it. By doing so all neurons were given the same structure of neighbors. We expected that all neurons then should---in theory---exhibit the exact same firing rate due to symmetry. Figure \ref{Fir_Rate_Dist_Reg_Grid} shows the simulation result, being a significantly narrower distribution. As predicted, the analytic result showed a similarly narrow distribution. This strongly supported the previous assertion.
\begin{figure}
\begin{center}
%% plot_firing_rate_dist_regular_grid.py
\includegraphics[width=0.7\textwidth]{../../plots/firing_rate_dists/regular_grid_firing_rate_dist.png}
\end{center}
\caption{Distribution of firing rates for a regular square grid with distance $\mathrm{50\, \mu m}$ and Neumann boundary conditions, $\mathrm{D=10\,\mu m^2 ms^{-1}}$, full simulation and analytic prediction. 1 Simulation run was used, with spikes within $\rm 1200 \leq t \leq 1500$.}
\label{Fir_Rate_Dist_Reg_Grid}
\end{figure}

\subsubsection{Low-Density Neighborhoods correlate with strong outgoing Connections}
In Section \ref{Section_Mean_outgoing_Weights} we stated that diffusive homeostasis allowed the network to develop few neurons with exceptionally strong outgoing weights. We found this effect to be present in neurons with an above-average firing rate. Moreover, the outcomes presented in Section \ref{Section_Rand_Mat_vs_Sim} suggest that the steady state of firing rates is strongly influenced by the spatial arrangement of excitatory neurons. Combining these two qualities led us the conclusion that one should be able to observe some relation between spatial structure and the emergence of ``driver neurons". More specifically, regions of neurons with above average firing rates should develop stronger outgoing connections. To get an intuitive understanding of what characterizes regions of above-average firing rates we interpreted the homeostatic condition in the high-neuron-density limit as an approximation of a continuous integral equation:
\begin{equation}
\int d^2 x' \rho(\mathbf{x}') r(\mathbf{x}') \psi(|\mathbf{x}-\mathbf{x}'|) = NO_0 \; , \; \forall \, \mathbf{x}
\label{Density_Limit_Hom}
\end{equation}
where $\mathrm{\rho(\mathbf{x})}$ is the local neuron density and $\mathrm{r(\mathbf{x})}$ the local firing rate. Here we assumed that our tissue is of infinite size and thus the integral is carried out over $\mathbb{R}^2$. In this form the solution for $\mathrm{r(\mathbf{x})}$ is quite trivial:
\begin{equation}
r(\mathbf{x}) = \frac{NO_0}{\rho(\mathbf{x}) \int d^2 x' \psi(|\mathbf{x}'|)} \propto \frac{1}{\rho(\mathbf{x})} \; .
\label{Density_Limit_Hom_Solution}
\end{equation}
Combined with the fact that the logarithm of outgoing excitatory weights correlates with excitatory firing rate (see Figure \ref{Out_Weight_vs_F}), this led us to the conclusion that low density regions should have strong outgoing weights and vice versa. We approximated the local neuron density by means of a a Gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$ to test this hypothesis. Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} shows the results. Despite a certain amount of randomness, our prediction was indeed verified. 
\begin{figure}
%% density_vs_sum_out_weights.py
\includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights.png}
%% density_vs_sum_out_weights_points.py
\includegraphics[width=\textwidth]{../../plots/scatter_density_out_weights_points.png}
\caption{A and B: Scatter plot of \emph{inverse} of local neuron density (calculated by convolution with a gaussian kernel with $\mathrm{\sigma = 50\, \mu m}$) and decadic logarithm of outgoing excitatory weights. Note the spatial correlation in high/low-density regions. C: Frequency of excitatory weights (averaged over $\rm 1200\,s \leq t \leq 1500\,s$) versus inverse neural density (same estimation method as in (A)). Coefficient of correlation $\rho_{\rm frequ.-dens.} = 0.798$. D: Decadic logarithm of mean outgoing excitatory weights versus inverse neural density. Coefficient of correlation $\rho_{\rm weight.-dens.} = 0.513$.}
\label{Inverse_Dens_vs_Sum_Out_Weights}
\end{figure}

\newpage
\subsection{Spreading of NO-sources extends Encoding of Input Heterogeneity}\label{NO_source_spread_section}
We considered the possibility that a wider spatial spread of each individual NO source---in contrast to the approximate point source used up to this point---could locally decrease distinguishability between neurons since our analytic results revealed that a strong correlation between spatial structure and resulting firing rates is present if diffusive interaction allows a clear distinction between individual neurons and their spatial neighbors. Referring to the results shown in Figure \ref{Ext_Input_Switch}, this modification with respect to the NO influx might allow input heterogeneities to be encoded over a longer period of time without the need to tweak diffusion to unrealistically high values. More specifically, one could potentially observe the distinction of input groups shown in Figure \ref{Ext_Input_Switch} over a longer time scale.  While Sweeney et al. argued that the size of the studied tissue is large compared to the size of individual somata (which, apparently, they claim to be the main source of nitric oxide) Philippides et al. reported that NO is often synthesized in a more delocalized way by means of fine fibers exceeding the soma \cite{Philippides_2005}. The diameter of these ``production areas" is on the order of $\mathrm{10-100 \mu m}$.

To test our hypothesis, we modified our model such that each neuron released nitric oxide evenly into a circular area with a radius of $\mathrm{50 \, \mu m}$, centered around the neuron's position. The homeostatic readout was still taken solely from the centering point. Thereafter, we ran the same simulation as for Figure \ref{Ext_Input_Switch}. Comparing both plots, we saw a much greater persistence of distinction between excitatory subgroups, see Figure \ref{External_Input_Switch_Spread_Source}. The time course of activity suggests that this distinction might even be permanent and steady instead of a very slow but transient state.
\begin{figure}
%% spread_source_illustration.py
\includegraphics[width=\textwidth]{../../plots/spread_source_illustration.png}
%% plot_external_input_switch_activity_spread_source.py
\includegraphics[width=\textwidth]{../../plots/external_input_switch_spread_source.png}
\caption{A/B: Illustration of circular kernels used for NO-insertion, overlay of all 400 neurons (left) and a single example (right). C: Resulting activity for excitatory subgroups. All settings were kept the same as for Figure \ref{Ext_Input_Switch}.}
\label{External_Input_Switch_Spread_Source}
\end{figure}

@@

\subsection{Homeostatic Stability}
Though being unintended in our recurrent network, the occurrence and necessary analysis of persistent oscillations led to a better understanding of their origin and the need for slow timescales of homeostatic adaptation. In another theoretical study Harnack et al. treated the necessity of slow homeostatic adaptation in a more general fashion \cite{Stability_Homeostasis_Harnack_2015}. Among other results it is reported that increasing the number of dynamic variables in a feedback system decreases its stability. This is in line with the fact that our previously used single-cell homeostatic control (see Equation \eqref{can_hom_rate}) exhibited no instabilities since it only incorporated firing thresholds as dynamic variables. In contrast, diffusive homeostasis increased the dimensionality of the system by means of its NO-synthesis and diffusion pathway. Harnack et al. additionally reported a similar effect as seen in our system: Noise can induce oscillations in a subscritical dynamical system by constantly causing deviations from its fixed point.

@@

Interestingly, Zenke, Hennequin and Gerstner theoretically investigated the interplay between Hebbian plasticity mechanisms and homeostatic processes that prevent runaway of synaptic efficacies and network activity \cite{Zenke_2013,Zenke_2017}. They came to the conclusion that regulatory mechanisms actually need to act on a time scale of at least minutes or seconds or faster to avoid dynamic instabilities such as persistent oscillations of activity and/or synaptic weights. It should however be noted that their research dealt with models of synaptic homeostasis rather than intrinsic mechanisms. Though it might seem so at first glance, we do not regard the findings by Zenke and Gerstner as necessarily contradicting those by Harnack et al., since the arguments brought forward do differ: While Zenke and Gerstner had to introduce a fast compensatory process mainly due to the self-potentiating effect of Hebbian plasticity rules, Harnack et al. only considered activity regulation in static networks. In a sense, while the former describes Hebbian plasticity as the source of instability that needs to be compensated by a fast homeostatic mechanism, the latter allocates the source of oscillatory instability within the homeostatic mechanism itself. This, however, might bring up the question why Zenke et al. did not as well observe similar instabilities as described by Harnack et al. when using relatively fast homeostasis in their network \cite{Zenke_2013}. A possible explanation could be that their feedback loop consists of a rather low-dimensional system that estimates firing rates through an exponential filter, keeping delays due to intermediate dynamic variables---a potential source of instability---small.

Furthermore, there is no reason to assume that fast synaptic homeostatic mechanisms could not act \emph{alongside} other slow activity-regulating processes. In fact, our network model also contained a form of fast synaptic homeostasis, though not regulating firing rates in a strict manner: Postsynaptic normalization, which was carried out once per second (see Section \ref{Section_Syn_Plast}) regulates synaptic efficacies on a time scale  that is in accordance to the findings by Zenke and Gerstner.

\subsection{The Firing Rate Distribution} \label{Fir_Rate_Dist_Discussion_Section}
By implementing diffusive homeostasis into the LIF-SORN model we managed to achieve a broader, skewed firing rate distribution while preserving appreciated features of network topology. Though the distribution did approximately resemble a log-normal-like shape, it did not perfectly match our expectations. In order to acquire a deeper understanding of the mechanisms that determine these statistics we derived an analytical expression that allowed us to reliably predict the steady state of firing rates based on the spatial structure of excitatory neurons. We would like to emphasize that this explanation differs from common approaches of understanding the emergence of heavy-tailed statistics of firing rates in recurrent networks. Theoretical studies on the behavior of recurrent networks are largely based on the assumption that the excitability of neurons is not individually fine-tuned but rather randomly distributed and adjusted globally to achieve a desired mean firing rate. Predictions about the resulting activity are then made based on (potentially simplified) statistical features of recurrent connectivity and the specific form of the neuronal transfer function used in the model, see e.g. \cite{Roxin_Firing_Rate_Distribution,Vreeswijk1998}. Our interpretation of our results leads to the conclusion that this canonical approach matches the limiting case of instant diffusion: While Figures \ref{Fir_Rate_Dist_Instant_compare} and \ref{Fir_Rate_Dist_Compare} did not reveal many differences in terms of overall statistics, the decorrelation discussed in Section \ref{Section_Rand_Mat_vs_Sim} and plotted in Figure \ref{Corr_Coeff_vs_D} suggests that increasing the diffusion constant goes along with a transition between a spatially determined configuration of excitatory firing rates and a network topology-determined behavior.

@@

Instead, we hypothesized that we might be able to uncouple activity from spatial structure without tweaking the diffusion process by spatially increasing the spread of NO-insertion. The result presented in Section \ref{NO_source_spread_section} was positive. Intuitively, this modification would allow to locally smear the distinction between neighboring neurons. From a more abstract point of view, it provides a way to drive the matrix defined in Equation \eqref{NO_equil_cond_interact_matrix_operator} towards singularity, allowing for more states of activity to approximately fulfill the homeostatic target. We therefore regard this idea as a potential modification for future use of diffusive homeostasis, gaining further control over the strictness of the homeostatic mechanism by adjusting the area of NO insertion.

@@

Taking a closer look at the distributions depicted in Figure \ref{Weight_Dist} we noted that the increased width of the distribution is largely due to an increment on the left half of the curve. Since new weights are initialized at $\mathrm{10^{-4}\, mV}$ this might indicate that some weights are drifting much more slowly from their value of initialization compared to other weights. These ``slow drifters" are presumably connecting neurons both spiking at a below-average firing rate.
This provides an explanation why this effect is more present in the case of diffusive homeostasis since it causes a portion of neurons to have rather low firing rates. On the other hand, for non-diffusive homeostasis, one can assume that the amount of STDP-fluctuations is approximately equal for all recurrent excitatory weights because of the fixation of firing rates.

@@

As an indirect consequence of spatial structure determining activity (as discussed in Section \ref{Fir_Rate_Dist_Discussion_Section}) we found that neurons with a low-density neighborhood have a higher chance of developing these strong outgoing weights. Since this effect is directly linked to the low-density/high-firing-rate relation shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (C), all previous thoughts regarding plausibility similarly apply to this result: \emph{If} a relationship between density and firing rates existed, we could indeed argue to also expect a relation as shown in Figure \ref{Inverse_Dens_vs_Sum_Out_Weights} (D), since it is known that synapses with above-average firing presynaptic neurons tend to undergo long-term potentiation \cite{Sjoestroem_Syn_Plasticity_2001,Feldman_STDP_2012}.
